---
title: "An Exemplary Title for an Academic Paper^[Thanks]"
subtitle: "An Informative Subtitle"
date: "`r format(Sys.Date(), '%B %Y')`"
output: 
  bookdown::word_document2:
    toc: no
    number_sections: yes
    global_numbering: true
    reference_docx: 'style_files/word_article.docx'
bibliography: 'references/bibliography.bib'
nocite: '@*'
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, 
    encoding = encoding, 
    output_file = paste0(substr(inputFile,1,nchar(inputFile)-4),"_",Sys.time(),'.docx'), 
    output_dir = "article/draft/")
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load("tidyverse", "flextable","officer","jtools")
source("scripts/helper.R")
```

::: {custom-style="Author"}
First Author,$^a$ Second Author,$^b$ and Third Author$^c$
:::

::: {custom-style="Institute"}
$^a$Institute, email@institute.edu

$^b$Institute, email@institute.edu

$^c$Institute, email@institute.edu
:::

::: {custom-style="Abstract-Heading"}
Abstract
:::

::: {custom-style="Abstract"}
*[Replace with your abstract]* This project, developed in RStudio and hosted on a GitHub repository, leverages the powerful capabilities of the Bookdown package to produce an academic paper in Microsoft Word format. The template provides a structured framework for composing, compiling, and publishing scholarly works, integrating features such as automatic reference and citation management, seamless inclusion of R code and outputs, versatile formatting, and efficient version control. 
:::

**Key Words:** Article template

# The YAML

This YAML header configures the primary attributes of the academic paper. 

This code is an example of a YAML header used in an R Markdown document. It contains information about the metadata and output specifications for the document:

- **Title & Subtitle**: The "title" and "subtitle" fields refer to the main title and subtitle of the academic paper respectively.

- **Date**: The "date" field uses R code inside a special inline code format to automatically generate today's date in a "Month Day, Year" format.

- **Output**: The "output" field specifies the output format. In this case, it's set to produce a Microsoft Word document (`bookdown::word_document2`), with no table of contents (`toc: no`), numbered sections (`number_sections: yes`), and global numbering (`global_numbering: true`). The output document styling is defined by a reference Word document located in 'style_files/word_article.docx'.

- **Bibliography**: The "bibliography" field links to a BibTeX file ('references/bibliography.bib') that contains the citation data.

- **Nocite**: The "nocite" field is set to '@*', which means all references in the .bib file will be included in the bibliography, regardless of whether they are cited in the text. If you do not want all reference included in the reference section, comment this line out.

- **Knit**: The "knit" field is a custom function for rendering the document. 

    - The output file name will include a timestamp: This is achieved with the command `output_file = paste0(substr(inputFile,1,nchar(inputFile)-4),"_",Sys.time(),'.docx')`. If you don't want the timestamp included in the file name, you can delete this argument.

    - The output file will be directed to the 'article/draft' folder: This is set by `output_dir = "article/draft/"`. If you want to change this to a different folder, for example 'article/final', you simply replace 'draft' with 'final'.

# Captions and Cross Referencing 

## Equations

See Equation \@ref(eq:mean).

\begin{equation}
\bar{X} = \frac{\sum_{i=1}^n X_i}{n} (\#eq:mean)
\end{equation}


## Figures 

See Figure \@ref(fig:cars-plot). 

```{r cars-plot, fig.cap="The cars data.", echo=FALSE}
par(mar = c(4, 4, .2, .1))
plot(cars)
```


`fig.cap="The cars data."` is used to add a caption to the figure, which reads "The cars data."

`\@ref(fig:cars-plot)` is a special syntax used in R Markdown to create a cross-reference to a figure. In this case, it creates a reference to the figure produced in the code chunk labeled `cars-plot`. Note that `fig:` is added to indicate that the crossref is to a figure.

The `@` symbol tells R Markdown that `ref(fig:cars-plot)` is a reference, and `fig:cars-plot` is the label of the code chunk that the figure comes from. When the R Markdown document is knit, `See Figure \@ref(fig:cars-plot)` will be replaced with something like "See Figure 1", where "1" is the automatically assigned number of the figure produced by the `cars-plot` chunk.


## Tables 

### knitr::kable()

See Table \@ref(tab:mtcars).

```{r mtcars, echo=FALSE}
knitr::kable(mtcars[1:5, 1:5], caption = "kable with crossref")
```

The `kable()` function allows the caption to be set directly. 

`\@ref(tab:mtcars)` the label mtcars comes from the chunk label

### flextable

See Table \@ref(tab:flextable)

::: {custom-style="Table Caption"}
<caption> (\#tab:flextable) Flextable with crossref </caption>
:::

```{r}
ft_basic(head(mtcars))
```


## jtools

See Table \@ref(tab:jtools)

::: {custom-style="Table Caption"}
<caption> (\#tab:jtools) jtools with crossref </caption>
:::

```{r jtools, message=FALSE,warning=FALSE}
fit <- lm(metascore ~ log(budget), data = movies)
fit_b <- lm(metascore ~ log(budget) + log(us_gross), data = movies)
fit_c <- lm(metascore ~ log(budget) + log(us_gross) + runtime, data = movies)
coef_names <- c("Budget" = "log(budget)", "US Gross" = "log(us_gross)",
                "Runtime (Hours)" = "runtime", "Constant" = "(Intercept)")
export_summs(fit, fit_b, fit_c, 
             robust = "HC3", 
             coefs = coef_names,
             align = ".",
             borders = 0.4,
             outer_borders = 2) %>% 
  huxtable::set_all_padding(3)
```



# Citations

Citation commands: \@sampleArticle is is Author (Year), i.e. @sampleArticle, and [\@sampleArticle] is (Author Year), i.e. [@sampleArticle].



::: {custom-style="Heading 1"}
References
:::

