---
title: "An Exemplary Title for an Academic Paper^[Thanks]"
subtitle: "An Informative Subtitle"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  bookdown::word_document2:
    toc: no
    number_sections: yes
    global_numbering: true
    reference_docx: 'style_files/word_article.docx'
bibliography: 'references/bibliography.bib'
nocite: '@*'
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, 
    encoding = encoding, 
    output_file = paste0(substr(inputFile,1,nchar(inputFile)-4),"_",Sys.time(),'.docx'), 
    output_dir = "article/draft/")
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load("tidyverse", "flextable","officer","crosstable")

```

::: {custom-style="Author"}
First Author,$^a$ Second Author,$^b$ and Third Author$^c$
:::

::: {custom-style="Institute"}
$^a$Institute, email@institute.edu

$^b$Institute, email@institute.edu

$^c$Institute, email@institute.edu
:::

::: {custom-style="Abstract-Heading"}
Abstract
:::

::: {custom-style="Abstract"}
*[Replace with your abstract]* This project, developed in RStudio and hosted on a GitHub repository, leverages the powerful capabilities of the Bookdown package to produce an academic paper in Microsoft Word format. The template provides a structured framework for composing, compiling, and publishing scholarly works, integrating features such as automatic reference and citation management, seamless inclusion of R code and outputs, versatile formatting, and efficient version control. 
:::

# Heading 1




## Heading 2



### Heading 3



#### Heading 4

# Cross Referencing


```{r, include=FALSE}
ft_basic <- function(df){
  ft <- df  %>%
    flextable() %>% 
    set_table_properties( layout = "autofit",
                          align = "center",
                          width = 1) %>%
    border_remove() %>%
    bold(part = "header") %>%
    hline_top(part = "header",border = fp_border(width = 2)) %>%
    hline_bottom(part = "header") %>%
    hline_bottom(part = "body" ,border = fp_border(width = 2)) #%>% 
    #set_caption(caption=caption,align_with_table = TRUE,word_stylename = "Caption",autonum = TRUE)
  return(ft)
}

```

## Figures 

See Figure \@ref(fig:cars-plot).

```{r cars-plot, fig.cap="The cars data.", echo=FALSE}
par(mar = c(4, 4, .2, .1))
plot(cars)  # a scatterplot
```

## Equations

See Equation \@ref(eq:mean).

\begin{equation}
\bar{X} = \frac{\sum_{i=1}^n X_i}{n} (\#eq:mean)
\end{equation}

## Tables 

See Table \@ref(tab:mtcars).

```{r mtcars, echo=FALSE}
knitr::kable(mtcars[1:5, 1:5], caption = "kable with crossref")
```

See Table \@ref(tab:flextable)

::: {custom-style="Table Caption"}
<caption> (\#tab:flextable) Flextable with crossref </caption>
:::

```{r}
ft_basic(head(mtcars))
```

# Citations

Citation commands: \@sampleArticle is is Author (Year), i.e. @sampleArticle, and [\@sampleArticle] is (Author Year), i.e. [@sampleArticle].



::: {custom-style="Heading 1"}
References
:::

